Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-01-20 Manuscript/Manuscript.Rmd
Add Heckman model function and notes

  - `region` Cluster variable,
  - `hiv` HIV diagnosis (0=no, 1=yes),
  - `age` Age of the patient,
  - `marital` Marital status,
  - `condom` Condom use during last intercourse,
  - `smoke` Smoker (levels).

>>>>

  - `region` Cluster variable,
  - `hiv` HIV diagnosis (0=no, 1=yes),
  - `age` Age of the patient,
  - `marital` Marital status,
  - `condom` Condom use during last intercourse,
  - `smoke` Smoker (levels; inclusion restriction variable).

There is a specific MNAR mechanism.

- main model = analysis model = predicting the prevalence of hiv
- people who have hiv are more reluctant to taking the test, not to reveal their status
- solution: take variables from analysis model like condom use, marital status, age, etc. that relate to hiv prevalence
- exclusion restriction variable = instrumental variable (from economics) = e.g. how kind the nurse was = smoke in this dataset = should be correlated to the missingness indicator, but *not* the variable itself
- include these variables in the selection equation
- take the missingness indicator of the variable of interest for the selection equation as DV
- heckman models estimate BOTH selection and mean models simultaneously, because linked through the error term
- if the errors are not correlated, the models are not linked at all -> not MNAR, but just MAR
- if the rho is significantly different from zero, the errors are correlated and the models are related so we have MNAR
- now, we add clustering
- copulas = estimate 2 equations separately and use another equation to link them
- for each of the clusters, est the copula separately, so we have all coeffs for each cluster, incl the rho and sigma (the errors)
- put together all of the estimates through a meta-analysis model to get population distribution of the estimates
- use the population parameter estimates to draw marginal parameters from the distribution to get a cluster/study parameter
- with systematical miss we can est the values of the imputed values based on the marginal distribution
- optional to add shrinkage: the marginal in account as well
- the hiv data was simulated by the copula function/model developer
- we could add a systematically missing variable in the data, because these are all sporadically
